---
title: "FIT File Reading Notes"
output: html_document
date: "2023-07-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, error=FALSE, cache = TRUE)
library(FITfileR)
library(tidyverse)
library(edwards)
library(kableExtra)
#library(slider)
source("../FUNC.R")
#theme_set(theme_minimal())
```

# Wahoo Elemnt Bolt

This is a file from 2022-06-05.

```{r, fit}
fit <- readRDS("../data_processed/eb_2022-06-05-084512.RDS")
fit2 <- readRDS("../data_processed/eb_2020-08-14-184117.RDS")
```

```{r, types, echo = TRUE}
listMessageTypes(fit)
count_message_types(fit) %>% my_kable()
```

Extracting "mfg_range_min" messages gives errors:

```{r, errs, echo = TRUE, error = TRUE}
getMessagesByType(fit, "device_info")
getMessagesByType(fit, "mfg_range_min")
```

In another file the "device_info" did work and produced a tibble with 16 rows. Here are 3 representative rows (I have shortened the names (device -> dev)):

```{r, dev_info}
  x <- getMessagesByType(fit2, "device_info") %>% 
    bind_rows() %>% 
    rename_with(~str_replace(., "device", "dev"))
  my_kable(slice(x, c(1,2,16)), caption = "device_info")
```
 
The remaining messages give the following sized tibbles (after `bind_rows()`):

```{r dims}
types <- listMessageTypes(fit)
use <- types %in% c("file_id", "hr_zone", "power_zone", "sport", "session", "lap", "record", "event", "workout", "activity")
#ind_use <- c(1:8, 10:12)
fit_list <- map(types[use], ~bind_rows(getMessagesByType(fit, .)))
names(fit_list) <- types[use]
fit_list$record <- arrange(fit_list$record, timestamp)
map(fit_list, ~dim(.)) %>%
  enframe() %>%
  hoist(value, nrow = 1, ncol = 2) %>% 
  my_kable()
```

There may be extra message types in some files, for example, "segment_lap" if strava live is enabled.

```{r segment lap}
  my_kable(getMessagesByType(fit2, "segment_lap"), caption = "segment_lap")
```

Here are the contents of the smaller of those tibbles (first 6 rows in the case of records):

```{r, results = "asis"}
use <- c("file_id", "hr_zone", "power_zone", "sport", "record", "event", "workout", "activity")
walk2(fit_list[use], names(fit_list[use]), ~print(my_kable(head(.x), caption = .y)))
```

The "session" data has all of the columns in the "lap" data plus these others:

```{r, sess_lap_cols}
setdiff(names(fit_list$session), names(fit_list$lap))
```

In this example there is only one lap so the single row in "lap" gives the same data as "session". Here is a `glimpse()` of the "session" table:

```{r}
glimpse(fit_list$session)
```

If there is no power meter then those columns will be missing. If there is a HRM then there will be extra columns relating to that.

